\section{Eligibility}
advisors must be a faculty member, a national official, an alumnus of Beta Epsilon with appropriate chapter experience, a graduate student with appropriate chapter experience, or a former chapter president. 

\section{Temporary Advisors}
Temporary advisors may be appointed by the President with the consent of $\frac{2}{3}$rds of the officer corps. Such temporary advisors shall serve until the next Election at which time they will stand for election. Upon confirmation by the officer corps, such advisors will have the rights and privileges of elected advisors. 

\section{Advisor Election}
%Advisors shall be elected following the same election procedure as officers, outlined in Appendix~\ref{app:elections}, except that both the incoming and outgoing president shall be able to comment on the merits of candidates. Since there is not a fixed number of positions for advisors, each advisor is elected individually; a vote to elect shall be considered to have passed if the candidate receives a majority of votes cast.

Advisors shall be elected at the officer transition meeting at the end of each semester.  Each advisor will be given five minutes to make a speech, followed by at most 3 minutes of questions and answers.  Then the candidates will leave the room, and the officers will discuss each candidate?s suitability for the position.  After this period of discussion, a vote will be called.  All incumbent officers and incoming officers get one vote.  If an officer is both incumbent and incoming, they still receive only one vote.  Since there is not a fixed number of positions for advisors, each advisor is elected individually; a vote to elect shall be considered to have passed if the candidate receives a majority of votes cast. 

\section{Advisor Term}
Advisor term length will be subject to motion from the floor as part of the election proceedings. An advisor candidate must indicate his/her preferred term length, and cannot be elected to a term longer than that. The maximum length for an individual term is three years. The term length is considered part of the motion to elect and therefore may be amended by the body. If an advisor fails to receive a majority of votes cast, a motion may be made to elect him/her to a shorter term, to a minimum of one semester.

\section{Responsibilities}
The advisors shall be responsible for:

\begin{enumsubsection}
\item{General} The advisors are responsible for ensuring chapter continuity. They should attend the chapter officer meetings and provide input to the president and other chapter officers.

\item{Vision Chair Selection} The advisors shall select from among themselves a chair for the Vision Committee.\label{sec:visionChair}

\item{Elections Chair Selection} The advisors shall select from among themselves a chair for the Elections meeting(s).

\item{Chapter Financial Advisor} The advisors shall select from among themselves a designated Chapter Financial Advisor, whose responsibilities including ensuring financial continuity, maintaining familiarity with the state of chapter finances and with the relevant financial processes (e.g., taxes), and advising the treasurer as needed.

\end{enumsubsection}