

\section{Amendment} These chapter bylaws may be amended upon the affirmative vote of two-thirds of the present and voting members at a regularly scheduled meeting, or by a one-half vote of the active membership at a special meeting, which must be announced at least one week in advance. Amendments will take effect immediately upon (a) approval from the active membership and (b) submission of these bylaws to the \hkn Executive Council the unless a motion is made at the time of approval to set an alternate date. The chapter can operate under the tentative assumed approval by the \hkn Executive Council until explicitly informed by the officer corps that portions of the submitted bylaws are not approved and require modifications.
\section{Appendix Amendments} Appendix~\ref{app:ugradreqs} (Undergraduate Initiation Requirements) and Appendix~\ref{app:gradreqs} (Graduate Initiation Requirements) may be modified at the discretion of the officer corps. Any other appendices may be amended upon the affirmative vote of two-thirds of the present and voting members at a regularly scheduled meeting, or by a simple majority vote of the active membership at a special meeting, which must be announced at least one week in advance.
\section{Adoption} Adoption of these chapter bylaws will immediately take place with the consent of a majority of the total active membership. Approval from the \hkn Executive Council is required pursuant to the \hkn Operations Manual. These bylaws will supersede any other Bylaws of this chapter.

