
\section{Accounts}
The chapter shall maintain a University or department account and, if approved by the Officer Corps, additional savings and/or checking accounts in a separate financial institution. Multiple accounts may be opened to separate funds from various chapter programs. No chapter assets shall be held in any account apart from these.

\section{Account Administration}
The treasurer will establish and administer all accounts. He/she has the sole authority to open accounts and to administer account signers.


\section{Account Name}
The name on the accounts must be ``Eta Kappa Nu''.

\section{\hkn Account Signers}
With the exception of accounts established for the purposes of operating the dB Caf\'{e}, the signers on the accounts shall be the President, Treasurer, and the Chapter Financial Advisor. A fourth signer, who should be the previous treasurer if possible, may be added at the discretion of the other three signers.

\section{dB Caf\'{e} Account Signers}
The signers on accounts established for the purposes of operating the dB Caf\'{e} shall be the President, Treasurer, Operations Officer, Chapter Financial Advisor, and the relevant officers from the local IEEE student branch, as determined by the local IEEE student branch President and by the contract between \hkn Beta Epsilon Chapter and the local IEEE student branch governing this relationship.

\section{\hkn Account Disbursement Limit}
With the exception of accounts established for the purposes of operating the dB Caf\'{e}, the signers on the accounts shall have the authority to issue disbursements equal to or under \$500. The Treasurer shall have the authority to issue disbursements from these accounts in amount up to and including \$5000.

\section{dB Caf\'{e} Disbursement Limit}
All actions involving accounts established for the purposes of operating the dB Caf\'{e} shall be governed by the contract between \hkn Beta Epsilon Chapter and the local IEEE student branch governing this relationship.

\section{Financial Report}
The Treasurer must prepare a financial report and budget at the beginning of each semester, consulting with the Chapter Financial Advisor. The budget must be prepared with input from the Officer Corps, and distributed to them upon completion.

\section{Audit}
The newly elected treasurer and the Chapter Financial Advisor must perform an audit of the chapter accounts and the Treasurer's records at the end of the Treasurer's term.

\section{Federal Employer Identification Number}
For accounts that require a Tax ID number, the Federal Employer Identification Number (FEIN) for Beta Epsilon chapter must be used. This FEIN is 38-6143476. Chapter accounts must not be established in any member's name, nor may they use the Social Security Number of any member or faculty advisor on the account.

\section{Tax Year}
The fiscal year for reporting revenue and expenses is July 1 through June 31.

