
\section{Initiation}
Candidates are initiated contingent on their completion of the initiation requirements to the satisfaction of the Officer Corps. The initiation requirements must be completed by the deadline(s) specified by the Vice President, which shall, in no case, be later than 48 hours prior to the initiation ceremony. The sole exception to this deadline is that candidates may complete the requirements after the deadline(s) if and only if they receive approval from the Vice President.

\section{Character Assesment}
Each candidate must be assessed for exemplary character as defined by the Officer Corps in Appendix \ref{app:ugradreqs} or \ref{app:gradreqs} as appropriate.

\section{Substitutions}
Each candidate must complete the minimum set of requirements as specified in Appendix \ref{app:ugradreqs} or \ref{app:gradreqs} as appropriate. Where circumstances merit, the Vice President may choose to allow any candidate to substitute one form of requirement for another, provided that the total number of hours completed is not diminished as a result of this.

\section{Waivers}
The officer corps, with a majority vote, may waive any requirement for any candidate, subject to majority approval by the Advisory Board.

\section{Deferral}
A candidate may defer completion of their requirements until a future semester by notifying the Vice President both at the time of deferral and during the intended semester of initiation. Service hours that the candidate has completed may be carried over to future semester(s). Any other requirements, such as meeting attendance and social requirements, must not be carried over between semesters. A deferred candidate must fulfill the academic and chapter requirements of the candidate's semester of initiation regardless of any past semesters.

