\chapter{Advisors}\label{sec:advisors}

\section{}
The chapter must maintain a minimum of four advisors including at least one faculty advisor who will serve as the chapter's chief advisor. An advisor must be an initiated member of Eta Kappa Nu or \hkn. The faculty advisor will be selected by the advisors and must be a current or emeritus member of the EECS faculty.

\section{}
The Advisory Board shall serve as the liaison(s) between the chapter and the University and are responsible for ensuring chapter continuity.

\section{}
The Advisory Board shall act as an advisory and judiciary committee to determine the advisability of any action taken or proposed by the chapter. Such action may be referred to it by a vote of the chapter or brought before it by a petition of a minority of the same, or the Board may review such action on its own initiative. All changes in the Constitution and Bylaws of a chapter must be submitted to and approved by the Advisory Board before going into effect. The Advisory Board, by a majority vote, may forbid any such action or change, subject to an appeal to the membership wherein a three-quarters majority vote of voting members shall be required to overturn a decision of the Advisory Board.

\section{}
Upon vacancy or the decision by the president to add additional faculty advisor(s), the Officer Corps, with input from the membership, shall select  new advisor(s) and confirm their willingness to serve as advisor(s) pending confirmation from the membership. A referendum vote on each advisor candidate must then be scheduled as the first order of business at the next regularly scheduled elections meeting. A referendum is considered to have passed if it attains a simple majority.

\section{}
Non-faculty advisors will be appointed and elected pursuant to the process outlined in the bylaws.

\section{}
The officer holding the position of Corresponding Secretary shall notify \hkn upon a change of chief advisor and must ensure that \hkn and the active membership of the chapter always has the name and contact information for the current advisor(s).

\section{}
Advisors must be invited to all general meetings, special meetings, officer meetings, and special events, but are not required to attend.

