\chapter{Charter, Authority, and Definitions}\label{sec:definitions}

\section{History}
This chapter is named the Beta Epsilon chapter of \hkn. It was installed on April 23, 1937 and is located at the University of Michigan, Ann Arbor.

\section{Scope}
This constitution shall govern the activities of this chapter in all matters not specifically provided for in the \hkn Operations and Process Manuals.

\section{Authority}
This chapter constitution and any bylaws adopted thereunder shall jointly serve as the Beta Epsilon chapter's Chapter Operations Manual.

\section{Definitions}
The following terms, when referenced in this constitution or in any subordinate documents, shall have the following meanings:
%\begin{compactenum}[1.]\itemsep4pt
\begin{enumsubsection}

\itemnotoc ''Active Member'' means an initiated member of \hkn that meets certain standards for involvement with the chapter, as defined in the bylaws.
\itemnotoc ''Advisory Board'' means the current set of chapter advisors and the chapter president, vice president, and recording secretary.
\itemnotoc ''Candidate'' means a person who has been duly invited by the chapter to join \hkn.
\itemnotoc ''College of Engineering'' and ''College'' refer to the University of Michigan -- Ann Arbor's College of Engineering.
\itemnotoc ''Constitution'' refers to this document.
\itemnotoc ''EECS'' refers to the Electrical Engineering and Computer Science department within the College.
\itemnotoc ''Engineering Student Government'' refers to the current student government that primarily represents students enrolled in the College of Engineering.
\itemnotoc ''Local IEEE Student Branch'' refers to the IEEE student branch located at the University of Michigan--Ann Arbor.
\itemnotoc ''Officer Corps'' refers to the set of current chapter officers and advisors.
\itemnotoc ''University'' refers to the University of Michigan--Ann Arbor.

\end{enumsubsection}
%\end{compactenum}

