\chapter{Chapter Membership}\label{sec:membership}


\section{}
Membership in \hkn is by invitation only. The specific criteria for offering and maintaining membership are provided in the \hkn Operations Manual as well as in the chapter bylaws.

\section{Removal}
A member may be removed from the society for performing an act detrimental to the Beta Epsilon chapter of \hkn. A motion to revoke membership will be raised only upon a three-fourths majority vote of the Officer Corps. Revoking membership requires a three-fourths majority vote of the present and voting membership at a general meeting and a three fourths affirmative vote of the Advisory Board.

\section{Quorum}
 Quorum for voting meetings shall be a simply majority of the active membership. The necessary participation required for a member to be considered active shall be defined in the bylaws.


\chapter{Candidates}\label{sec:candidates}

\section{}
A candidate may be blocked from initiating into the society for performing an act detrimental to the Beta Epsilon chapter of \hkn or demonstrating poor character, regardless of their progress in electing. A motion to block initiation shall not be raised without a three-fourths majority vote of the Officer Corps in favor. Blocking initiation requires a three-fourths affirmative vote of the present and voting membership at a general meeting and three-fourths affirmative vote of the Advisory Board. If the motion is successful, the candidate cannot be initiated into the Beta Epsilon chapter of \hkn that semester, and will not be eligible for initiation  in subsequent semesters until a majority vote of the Officer Corps overturns the decision.

\chapter{Officers}\label{sec:officers}

\section{}
The minimum set of chapter officers is defined in the \hkn Operations Manual. Additional responsibilities of the required officers, as well as additional officer positions, may be specified in the chapter bylaws.

\section{}
The officer corps has the power to make decisions affecting the day-to-day operation of the chapter between and during regularly scheduled chapter meetings. Decisions not specifically delegated to an individual officer by the constitution or bylaws will be made by a simple majority vote of the officer corps.

\section{}
Regular elections must be held once per each Fall and Winter academic semester. The elections meeting must be announced to both active members and potential initiates at least one week in advance in the manner typical for chapter announcements. Specific election procedures, including but not limited to time limits and order of individual elections, may be defined in the chapter bylaws.

\section{}
Newly elected officers shall take office at midnight on the first day following the exam period of the semester within which the election took place.

\section{Removal}
 An officer may be removed from office for failing to perform his/her duties or for performing an act detrimental to Beta Epsilon chapter of \hkn. A motion to remove an officer will be raised only upon a three-fourths majority of the remaining Officer Corps. Removing an officer requires a three-fourths majority vote of the present and voting members at a general meeting and a three fourths affirmative vote of the Advisory Board .

